---
title: "Rotate netCDF data"
author: "Just Berkhout"
date: "11/21/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)



```

## LME Plot

The data is encoded in degrees, starting from -180º to 180º

```{r lmeplot, echo=FALSE}
LMEs <- rgdal::readOGR(dsn ="/rd/gem/private/fishmip_inputs/misc/LMEs66/", layer = "LMEs66", verbose = FALSE)
ElevenColours = RColorBrewer::brewer.pal(11, "Set3")
plot(LMEs, col=ElevenColours[LMEs$LME_NUMBER%%11], border="white", lwd=1, axes=T, ylim = c(-90, 90) )
```

## Brick from netCDF plotted
The netCDF data is encoded from 0º to 360º

this means that the eastern hemisphere (0º to 180º) aligns with the LME polygons, but the western hemisphere does not (181º to 360º doesn't work against -180 to 0º).


```{r brick, echo=FALSE}
my_brick <- raster::brick("/rd/gem/private/GCM_INPUT/IPSL_CM5A_LR/rcp26/ipsl-cm5a-lr_rcp26_lphy_zint_monthly_200601_21001231.nc4")
plot(my_brick[[1]]) #plots the firstlayer of the world lphy brick
```


## Brick from netCDF rotated
The netcdf data neds to be manipuated using `raster::rotate()` to align with the 
polygon data of the LMEs to ensure cropping gets to the correct data for both eastern and western hemispheres. 

```{r brickrotated, echo=TRUE}
my_brick_rotated <- raster::rotate(my_brick) #change coords from 0 to 360 to -180 to 180
```

```{r plotbrickrotated, echo=FALSE}
plot(my_brick_rotated[[1]]) #plots the firstlayer of the world lphy brick
```